Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-03-24 RR_manuscript/Draft_RR.Rmd
:sparkles: - update links

<!-- TODO: add LINK to survey -->
The analysis teams will register and answer a demographic and expertise survey (LINK).
The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We will then request that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.^[See <https://osf.io/rdtx5/?view_only=66989a3bbe034e188846e23f84913ffe>. Due to storage caps on the OSF, we will make the audio files available on <https://eudat.eu/catalogue/B2SHARE> in due course.]

<!-- TODO: add LINK to analytic survey -->
Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to analyses from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
<!-- TODO: add LINK to peer review survey -->
The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
We will also archive copies of our survey instruments from analysts and peer reviewers.

>>>>

The analysis teams will register and answer a demographic and expertise questionnaire (`intake_form.pdf`).^[PDF versions of all the questionnaires mentioned in this paper are available at <https://github.com/many-speech-analyses/many_analyses/tree/master/docs/questionnaires>.]
The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We will then request that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.^[See <https://osf.io/rdtx5/?view_only=66989a3bbe034e188846e23f84913ffe>. Due to storage caps on the OSF, we will make the audio files available on <https://eudat.eu/catalogue/B2SHARE> in due course.]

Once their analysis is complete, they will answer a structured questionnaire (`analytical_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to analyses from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
Each peer reviewer will register and answer a demographic and expertise questionnaire identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
The reviewer will then be asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer reviewers.
Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
We will also archive copies of our survey instruments from analysts and peer reviewers.

### 2021-03-24 RR_manuscript/Draft_RR.tex
:sparkles: - update links

The analysis teams will register and answer a demographic and expertise survey (LINK).
The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.\footnote{See \url{https://osf.io/rdtx5/?view_only=66989a3bbe034e188846e23f84913ffe}. Due to storage caps on the OSF, we will make the audio files available on \url{https://eudat.eu/catalogue/B2SHARE} in due course.}

Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to analyses from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).
Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
We will also archive copies of our survey instruments from analysts and peer reviewers.

>>>>

The analysis teams will register and answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).\footnote{PDF versions of all the questionnaires mentioned in this paper are available at \url{https://github.com/many-speech-analyses/many_analyses/tree/master/docs/questionnaires}.}
The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.\footnote{See \url{https://osf.io/rdtx5/?view_only=66989a3bbe034e188846e23f84913ffe}. Due to storage caps on the OSF, we will make the audio files available on \url{https://eudat.eu/catalogue/B2SHARE} in due course.}

Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytical\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to analyses from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
Each peer reviewer will register and answer a demographic and expertise questionnaire identical to that asked of the analysts.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).
Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer reviewers.
Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
We will also archive copies of our survey instruments from analysts and peer reviewers.
